Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-11-11 paper/paper.tex
update intro

Despite their widespread use, purely linguistic references to timbre fail to convey the intention of the composer.
On the one hand, adjectives such as \emph{bright} or \emph{rough} are prone to misunderstanding, as they do not prescribe any musical gesture that is capable of achieving them \cite{antoine2018isma}.
On the other hand, the sole mention of a playing technique does not determine any intended effect; as a result, it fails to generalize to the entire instrumentarium \cite{kolozali2011ismir}.
For instance, although the term \emph{breathy} alludes to a playing technique that is peculiar to wind instruments, a cellist may accomplish a seemingly breathy timbre by bowing near the fingerboard, i.e., \emph{sul tasto} in the classical terminology.

>>>>

Despite their widespread use, purely linguistic references to timbre fail to convey the intention of the composer.
On the one hand, adjectives such as \emph{bright} or \emph{rough} are prone to misunderstanding, as they do not prescribe any musical gesture that is capable of achieving them \cite{antoine2018isma}.
On the other hand, the sole mention of a playing technique does not determine any intended effect; as a result, it does not generalize to the entire instrumentarium \cite{kolozali2011ismir}.
For instance, although the term \emph{breathy} alludes to a playing technique that is peculiar to wind instruments, a cellist may accomplish a seemingly breathy timbre by bowing near the fingerboard, i.e., \emph{sul tasto} in the classical terminology.
